Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-05-14 paper/ijcai/paper.tex
acks
small fixes

Figure~\ref{fig:boxplot} shows the distributions of $\Delta{}C$ considering all the 
cases where the predicate $\Delta{}C>0$ holds, \ie{}, it focuses only
on the cases \combpar{k} outperformed the baseline technique.
To sum, although we observed a relatively small number of cases where $\Delta{}C$
is negative (\numOutPerformed) and a high number of cases where $\Delta{}C$
is zero (\numEquallyPerformed), there is a
considerable amount of cases where $\Delta{}C$ is positive and for
those cases \combpar{k} seems very beneficial.
% On the left-hand-side, we show distributions of
% $\Delta{}C$, for different values of $k$, considering all cases where
% the predicate $\Delta{}C\geq{}0$ holds, \ie{}, we excluded the
% \numOutPerformed\ cases where \sfl{}$^{k}$ outperformed \combpar{k}
% (see Figure~\ref{fig:diagnosis}).

@@

Table \ref{table:st} presents the statistics to determine if the
observed results are statistically significant. Shapiro-Wilk tests the
null hypothesis that results are drawn from a normal distribution. The
test is performed for all techniques and values of $k$. With $99\%$
confidence, the results tell us that the distributions are not
normal. Given that $C$ is not normally distributed, we used Friedman, a
non-parametric statistical test of hypothesis. The null hypothesis is
that the rankings obtained with all techniques and variants are the
same. With $99\%$ confidence, the results show that the distributions
are distinct. To understand which techniques perform differently,
\ie{}, to answer the question \textit{Does \combpar{k} perform
  differently than \sfl{}$^{k}$}, we performed a Siegel post-hoc
analysis. Figure \ref{fig:performance} reports results. Each square
shows the statistical significance of the difference in diagnostic
accuracy amongst the different techniques--the lighter color and
smaller value of $p$ indicates higher significance. Based on these
results, it is possible to determine with $95\%$ confidence that the
performance of each pair of techniques is different.

@@

>>>>

Figure~\ref{fig:boxplot} shows the distributions of $\Delta{}C$ considering all the 
cases where the predicate $\Delta{}C>=0$ holds, \ie{}, it focuses only
on the cases where \combpar{k} outperformed the baseline technique in at least one $k$.
To sum, although we observed a relatively small number of cases where $\Delta{}C$
is negative (\numOutPerformed) and a high number of cases where $\Delta{}C$
is zero (\numEquallyPerformed), there is a
considerable amount of cases where $\Delta{}C$ is positive and for
those cases \combpar{k} seems very beneficial.
% On the left-hand-side, we show distributions of
% $\Delta{}C$, for different values of $k$, considering all cases where
% the predicate $\Delta{}C\geq{}0$ holds, \ie{}, we excluded the
% \numOutPerformed\ cases where \sfl{}$^{k}$ outperformed \combpar{k}
% (see Figure~\ref{fig:diagnosis}).

@@

Table \ref{table:st} presents the statistics to determine if the
observed results are statistically significant. Shapiro-Wilk tests the
null hypothesis that results are drawn from a normal distribution. The
test is performed for all techniques and values of $k$. With $99\%$
confidence, the results tell us that the distributions are not
normal. Given that $C$ is not normally distributed, we used Friedman, a
non-parametric statistical test of hypothesis. The null hypothesis is
that the rankings obtained with all techniques and variants are the
same. With $99\%$ confidence, the results show that the distributions
are distinct. To understand which techniques perform differently,
\ie{}, to answer the question \textit{Does \combpar{k} perform
  differently than \sfl{}$^{k}$}, we performed a Siegel post-hoc
analysis. Figure \ref{fig:performance} reports results. Each square
shows the statistical significance of the difference in diagnostic
accuracy amongst the different techniques--the lighter color means no
statistical significance and smaller values of $p$ indicates higher significance. 
Based on these results, it is possible to determine with $95\%$ confidence that the
performance of each pair of techniques is different (except for \combpar{5} 
versus \combpar{10}, where there is no significance).

@@

This material is based upon work supported by Fundação para a Ciência e a Tecnologia (FCT), with the reference PTDC/CCI-COM/29300/2017.
